The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-24 paper/paper.tex
Experimenting coht -> coh2
Missing arguments, refinements, typos...

\newcommandx{\deps}[2][1,2]{\depsmacro{deps}{restr}{russian-green}[#1][#2]}
\newcommandx{\fulldeps}[1][1]{\depsmacro{deps}{fullrestr}{russian-green}[#1]}
\newcommandx{\depscohs}[2][1,2]{\depsmacro{deps}{coh}{chestnut}[#1][#2]}
\newcommandx{\fulldepscohs}[1][1]{\depsmacro{deps}{fullcoh}{chestnut}[#1]}
\newcommandx{\depscoht}[2][1,2]{\depsmacro{deps}{coht}{chestnut}[#1][#2]}
\newcommandx{\fulldepscoht}[1][1]{\depsmacro{deps}{fullcoht}{chestnut}[#1]}
\newcommandx{\depstype}[2][1,2]{\depsmacro{DEPS}{restr}{russian-green}[#1][#2]}
\newcommandx{\fulldepstype}[1][1]{\depsmacro{DEPS}{fullrestr}{russian-green}[#1]}
\newcommandx{\depscohstype}[2][1,2]{\depsmacro{DEPS}{coh}{chestnut}[#1][#2]}
\newcommandx{\fulldepscohstype}[1][1]{\depsmacro{DEPS}{fullcoh}{chestnut}[#1]}
\newcommandx{\depscohttype}[2][1,2]{\depsmacro{DEPS}{coht}{chestnut}[#1][#2]}
\newcommandx{\fulldepscohttype}[1][1]{\depsmacro{DEPS}{fullcoht}{chestnut}[#1]}

@@

\begin{equation*}
  \begin{array}{llcl}
    \depstype[n][\lbrack 0,p-1 \rbrack]    &        & \defeq                               &
    \left(\begin{array}{lll}
              \framep[n][\lbrack 0,p-1 \rbrack]   & : & \frametype[n][\lbrack 0,p-1 \rbrack]    \\
              \painting[n][\lbrack 0,p-1 \rbrack] & : & \paintingtype[n][\lbrack 0,p-1 \rbrack]
              (\framep[n][\lbrack 0,p-1 \rbrack])                                               \\
              \restrf[n][\lbrack 0,p-1 \rbrack]   & : & \restrftype[n][\lbrack 0,p-1 \rbrack]
              \left(\begin{array}{l}
                  \framep[n][\lbrack 0,p-1 \rbrack]   \\
                  \painting[n][\lbrack 0,p-1 \rbrack] \\
                \end{array}\right)                                         \\
            \end{array}\right)  \\
    \framep[n+1][\lbrack 0,p \rbrack]      &
    \deps[n][\lbrack 0,p-1 \rbrack]        & :      & \frametype[n+1][\lbrack 0,p \rbrack]   \\
    \framep[n+1][\lbrack 0,0 \rbrack]      &
    \unitpoint                             & \defeq & (\unitpoint,\unittype)                 \\
    \framep[n+1][\lbrack 0,p+1 \rbrack]    &
    \deps[n][\lbrack 0,p \rbrack]          & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][\lbrack 0,p \rbrack]
              (\deps[n][\lbrack 0,p-1 \rbrack]), \\
              \Sigma d:\framep[n+1][p]
              (\deps[n][\lbrack 0,p-1 \rbrack]).
              \, \layer[n][p]
              (\deps[n][\lbrack 0,p \rbrack])
              (d)                                \\
            \end{array}\right)                                                 \\
    \restrftype[n][\lbrack 0,p-1 \rbrack]  &
    \left(\begin{array}{l}
              \framep[n][\lbrack 0,p-1 \rbrack]   \\
              \painting[n][\lbrack 0,p-1 \rbrack] \\
            \end{array}\right) & :      & \U                                                \\
    \restrftype[n]                         &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)                 & \defeq &
    \unittype                                                                                \\
    \restrftype[n][\lbrack 0,p \rbrack]    &
    \left(\begin{array}{l}
              \framep[n][\lbrack 0,p \rbrack]   \\
              \painting[n][\lbrack 0,p \rbrack] \\
            \end{array}\right)   & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n][\lbrack 0,p-1 \rbrack]
      :\restrftype[n][\lbrack 0,p-1 \rbrack]
      \left(\begin{array}{l}
                \framep[n+1][\lbrack 0,p-1 \rbrack]   \\
                \painting[n+1][\lbrack 0,p-1 \rbrack] \\
              \end{array}\right).         \\
      \Pi q \leq n-p.\,\Pi \epsilon.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n][\lbrack 0,p-1 \rbrack]   \\
                \painting[n][\lbrack 0,p-1 \rbrack] \\
                \restrf[n][\lbrack 0,p-1 \rbrack]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array}                       \\
    \layertype[n][p]                       &
    \deps[n][\lbrack 0,p \rbrack]
                                           & :      & \U                                     \\
    \layertype[n][p]                       &
    \deps[n][\lbrack 0,p \rbrack]
                                           & \defeq & \framep[n+1][p]
    (\deps[n][\lbrack 0,p-1 \rbrack])
    \rightarrow \U                                                                           \\
    \layer[n][p]                           &
    \deps[n][\lbrack 0,p \rbrack]
                                           & :      & \layertype[n][p]
    (\deps[n][\lbrack 0,p \rbrack])
    \\
    \layer[n][p]                           &
    \deps[n][\lbrack 0,p \rbrack]
                                           & \defeq &
    d \mapsto \Pi\epsilon.\,\painting[n][p](\restrf[n][p][0][\epsilon](d))                   \\
  \end{array}
\end{equation*}

@@

Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n]$, abbreviating this and the dependency in a $\coht[n][\lbrack 0,p-1 \rbrack]$ as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$. It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$. Thus, we also include this abbreviation in the definition:

@@

      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.                                                            \\
      \Pi d.\Pi l. {(\restrl[n][p][q][\epsilon](\restrl[n][p][r][\omega](l)))} =_{\cohf[n][p][r+1][q+1][\epsilon][\omega]} \\
      \restrl[n][p][r][\omega](\restrl[n][p][q+1][\epsilon](l))

@@

      \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])}                                                                                         \\
      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta]} (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])} (\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\

@@

      \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.                                                          \\
      \cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) \circ \\

@@

      (\depscoht[n][p]))

@@

      \cohf[n][p][q][r][\epsilon][\omega](\restrf[n+2][p][0][\theta](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))) =       \\

@@

      \cohf[n][p][q][0][\epsilon][\theta](\restrf[n+2][p][r+1][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack])))

@@

and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument of $\restrp$ and the deps argument)

@@

to

@@

      (\overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]}\restrp[n+1][p][r][\omega](l_\theta)))

@@

      (\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]}\restrp[n+1][p][q+1][\epsilon](l_\theta)))

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohp[n+1][p]                                &
    \fulldepscoht[n]                             & :      &
    \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                                \\
    \cohp[n+1][n+1][q][r][\epsilon][\omega]      &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c). l_\epsilon \\
    \cohp[n+1][p \leq n][q][r][\epsilon][\omega] &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \cohl[n][p][q][r][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
              \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c)              \\
            \end{array}\right)        \\
  \end{array}
\end{equation*}

From which we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$ again by a second recursion, this time on $p$:

@@

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$.
  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
  \item $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ comes from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
\end{itemize}

>>>>

\newcommandx{\deps}[2][1,2]{\depsmacro{deps}{restr}{russian-green}[#1][#2]}
\newcommandx{\fulldeps}[1][1]{\depsmacro{deps}{fullrestr}{russian-green}[#1]}
\newcommandx{\depscohs}[2][1,2]{\depsmacro{deps}{coh}{chestnut}[#1][#2]}
\newcommandx{\fulldepscohs}[1][1]{\depsmacro{deps}{fullcoh}{chestnut}[#1]}
\newcommandx{\depscoht}[2][1,2]{\depsmacro{deps}{coh2}{chestnut}[#1][#2]}
\newcommandx{\fulldepscoht}[1][1]{\depsmacro{deps}{fullcoh2}{chestnut}[#1]}
\newcommandx{\depstype}[2][1,2]{\depsmacro{DEPS}{restr}{russian-green}[#1][#2]}
\newcommandx{\fulldepstype}[1][1]{\depsmacro{DEPS}{fullrestr}{russian-green}[#1]}
\newcommandx{\depscohstype}[2][1,2]{\depsmacro{DEPS}{coh}{chestnut}[#1][#2]}
\newcommandx{\fulldepscohstype}[1][1]{\depsmacro{DEPS}{fullcoh}{chestnut}[#1]}
\newcommandx{\depscohttype}[2][1,2]{\depsmacro{DEPS}{coh2}{chestnut}[#1][#2]}
\newcommandx{\fulldepscohttype}[1][1]{\depsmacro{DEPS}{fullcoh2}{chestnut}[#1]}

@@

\begin{equation*}
  \begin{array}{llcl}
    \depstype[n][\lbrack 0,p-1 \rbrack]    &        & \defeq                               &
    \left(\begin{array}{lll}
              \framep[n][\lbrack 0,p-1 \rbrack]   & : & \frametype[n][\lbrack 0,p-1 \rbrack]    \\
              \painting[n][\lbrack 0,p-1 \rbrack] & : & \paintingtype[n][\lbrack 0,p-1 \rbrack]
              (\framep[n][\lbrack 0,p-1 \rbrack])                                               \\
              \restrf[n][\lbrack 0,p-1 \rbrack]   & : & \restrftype[n][\lbrack 0,p-1 \rbrack]
              \left(\begin{array}{l}
                  \framep[n][\lbrack 0,p-1 \rbrack]   \\
                  \painting[n][\lbrack 0,p-1 \rbrack] \\
                \end{array}\right)                                         \\
            \end{array}\right)  \\
    \framep[n+1][\lbrack 0,p \rbrack]      &
    \deps[n][\lbrack 0,p-1 \rbrack]        & :      & \frametype[n+1][\lbrack 0,p \rbrack]   \\
    \framep[n+1][\lbrack 0,0 \rbrack]      &
    \unitpoint                             & \defeq & (\unitpoint,\unittype)                 \\
    \framep[n+1][\lbrack 0,p+1 \rbrack]    &
    \deps[n][\lbrack 0,p \rbrack]          & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][\lbrack 0,p \rbrack]
              (\deps[n][\lbrack 0,p-1 \rbrack]), \\
              \Sigma d:\framep[n+1][p]
              (\deps[n][\lbrack 0,p-1 \rbrack]).
              \, \layer[n][p]
              (\deps[n][\lbrack 0,p \rbrack])
              (d)                                \\
            \end{array}\right)                                                 \\
    \restrftype[n][\lbrack 0,p-1 \rbrack]  &
    \left(\begin{array}{l}
              \framep[n][\lbrack 0,p-1 \rbrack]   \\
              \painting[n][\lbrack 0,p-1 \rbrack] \\
            \end{array}\right) & :      & \U                                                \\
    \restrftype[n]                         &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)                 & \defeq &
    \unittype                                                                                \\
    \restrftype[n][\lbrack 0,p \rbrack]    &
    \left(\begin{array}{l}
              \framep[n][\lbrack 0,p \rbrack]   \\
              \painting[n][\lbrack 0,p \rbrack] \\
            \end{array}\right)   & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n][\lbrack 0,p-1 \rbrack]
      :\restrftype[n][\lbrack 0,p-1 \rbrack]
      \left(\begin{array}{l}
                \framep[n+1][\lbrack 0,p-1 \rbrack]   \\
                \painting[n+1][\lbrack 0,p-1 \rbrack] \\
              \end{array}\right).         \\
      \Pi q \leq n-p.\,\Pi \epsilon.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n][\lbrack 0,p-1 \rbrack]   \\
                \painting[n][\lbrack 0,p-1 \rbrack] \\
                \restrf[n+1][\lbrack 0,p-1 \rbrack]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array}                       \\
    \layertype[n][p]                       &
    \deps[n][\lbrack 0,p \rbrack]
                                           & :      & \U                                     \\
    \layertype[n][p]                       &
    \deps[n][\lbrack 0,p \rbrack]
                                           & \defeq & \framep[n+1][p]
    (\deps[n][\lbrack 0,p-1 \rbrack])
    \rightarrow \U                                                                           \\
    \layer[n][p]                           &
    \deps[n][\lbrack 0,p \rbrack]
                                           & :      & \layertype[n][p]
    (\deps[n][\lbrack 0,p \rbrack])
    \\
    \layer[n][p]                           &
    \deps[n][\lbrack 0,p \rbrack]
                                           & \defeq &
    d \mapsto \Pi\epsilon.\,\painting[n][p](\restrf[n][p][0][\epsilon](d))                   \\
  \end{array}
\end{equation*}

@@

Thanks to $\cohptype[n][\lbrack 0,p-1 \rbrack]$, we can mutually define $\cohf[n+1][\lbrack 0,p \rbrack]$ and $\cohttype[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$ from $\fulldepscohs[n]$, abbreviating this and the dependency in a $\coht[n][\lbrack 0,p-1 \rbrack]$ as $\depscohttype[n][\lbrack 0,p-1 \rbrack]$, and using also abbreviations in passing for $\cohl$ and $\cohltype$. It is also convenient to build $\depscohs[n+1][\lbrack 0,p \rbrack]$ from $\depscoht[n][\lbrack 0,p-1 \rbrack]$, so that we can now build $\framep[n+3][p]$. Thus, we also include this abbreviation in the definition. Implicitly using in $\cohf[n+1][\lbrack 0,p \rbrack]$ that equalities in a $\Sigma$-type are equivalent to a $\Sigma$-type of the underlying equalities, we altogether have:

@@

      \Pi q \leq n-p.\,\Pi r\leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi d.\,\Pi l.                                                             \\
      \restrl[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][r][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))\\ =_{\cohf[n+1][p][r+1][q+1][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])} \\
      \restrl[n][p][r][\omega](\depscohs[n][\lbrack 0,p-1 \rbrack])(\restrl[n+1][p][q+1][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p-1 \rbrack]))(l))

@@

      \lambda d. \lambda l. \lambda \theta. \overrightarrow{\coht[n][p][q][r][\epsilon][\omega][\theta](\fulldepscohs[n])(d)}                                                                                         \\
      (\ap \overrightarrow{\cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d))}\\ (\ap \overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)} \\(\cohp[n][p][q][r][\epsilon][\omega](l_\theta)))) \\

@@

      \Pi q \leq n-p.\,\Pi r \leq q.\,\Pi \epsilon.\,\Pi \omega.\,\Pi \theta.\,\Pi d.                                                          \\
      \cohf[n][p][r][0][\omega][\theta](\restrf[n+2][p][q+2][\epsilon](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d)) \circ \\

@@

      (\depscoht[n][p])(d))

@@

      \cohf[n][p][q][r][\epsilon][\omega](\restrf[n+2][p][0][\theta](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d)) =       \\

@@

      \cohf[n][p][q][0][\epsilon][\theta](\restrf[n+2][p][r+1][\omega](\overline{\depscohs}(\depscoht[n][\lbrack 0,p \rbrack]))(d))

@@

and where the functoriality of equality and transport was used to go from (omitting the $\framep$ argument of $\restrp$ and the deps argument):

@@

to:

@@

      (\overrightarrow{\cohf[n+1][p][r][0][\omega][\theta]}(\restrp[n+1][p][r][\omega](l_\theta))))

@@

      (\overrightarrow{\cohf[n+1][p][q+1][0][\epsilon][\theta]}(\restrp[n+1][p][q+1][\epsilon](l_\theta))))

@@

\begin{equation*}
  \begin{array}{llcl}
    \cohp[n+1][p]                                &
    \fulldepscoht[n]                             & :      &
    \cohptype[n+1][p](\overline{\fulldepscohs}(\fulldepscoht[n]))                                \\
    \cohp[n+1][n+1][q][r][\epsilon][\omega]      &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c). l_\epsilon \\
    \cohp[n+1][p \leq n][q][r][\epsilon][\omega] &
    \fulldepscoht[n]
                                                 & \defeq & \lambda d. \lambda (l,c).
    \left(\begin{array}{l}
              \cohl[n][p][q][r][\epsilon][\omega](\depscoht[n][\lbrack 0,p-1 \rbrack])(d)(l), \\
              \cohp[n+1][p+1][q][r][\epsilon][\omega](\fulldepscoht[n])(d,l))(c)              \\
            \end{array}\right)        \\
  \end{array}
\end{equation*}
where we again implicitly used that equalities in a $\Sigma$-type are equivalent to a $\Sigma$-type of the underlying equalities, componentwise.

From the latter we can deduce $\cohp[n+1][\lbrack 0,p-1 \rbrack]$ for $p \leq n+2$, again by a second recursion, this time on $p$:

@@

Indeed, to build this structure at level $n+1$, from level $n$, it is
enough to assume $E:\framep[n+1][n+1](\deps[n][\lbrack 0,n \rbrack]) \rightarrow \U$ (where $\deps[n][\lbrack 0,n \rbrack]$ come from the assumptions at level $n$) and to build the following:
\begin{itemize}
  \item $\framep[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\deps[n][\lbrack 0,n \rbrack]$.
  \item $\painting[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\fulldeps[n](E)$.
  \item $\restrf[n+1][\lbrack 0,n+1 \rbrack]$ comes from $\depscohs[n][\lbrack 0,n \rbrack](E)$.
  \item $\restrp[n+1][\lbrack 0,n+1 \rbrack](E')$, for $E':\framep[n+2][n+2](\overline{\deps}(\depscohs[n][\lbrack 0,n \rbrack])) \rightarrow \U$, comes from $\fulldepscohs[n](E)(E')$.
  \item we define $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ from $\fulldepscohs[n](E)(E')$ and $\cohp[n][\lbrack 0,n \rbrack](E)(E')$.
  \item $\cohf[n+1][\lbrack 0,n+1 \rbrack](E')$ comes from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$.
  \item we define $\fulldepscoht[n](E)(E')(E'')$, for $E'': \framep[n+3][n+3](\overline{\deps}(\overline{\depscohs}(\depscoht[n][\lbrack 0,n \rbrack]))) \rightarrow \U$, from $\depscoht[n][\lbrack 0,n \rbrack](E)(E')$ and $E''$.
  \item $\cohp[n+1][\lbrack 0,n+1 \rbrack](E')(E'')$ comes from $\fulldepscoht[n](E)(E')(E'')$.
\end{itemize}
